%\chapter*{\large СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ}
\begin{thebibliography}{99}
\bibitem{alberta} Schmidt Alfred. Design of Adaptive Finite Element Toolbox ALBERTA /Scmidt Alfred, Siebert Kunibert~G. --- Berlin:Springer, 2006.---324c.
\bibitem{tetgen} Han Si. TetGen. A Quality Tetrahedral Mesh Generator and 3D Delaunay Triangulator. --- Berlin: WIAS , 2020 --- 95c.
\bibitem{triangle} Shewchuck Jonathan Richard. Triangle: Engineering a 2D Quality Mesh Generator and Delaunay Triangulator. --- Pittsburgh:Carnegie Mellon University,2005.---10c.
\bibitem{paraview} Moreland Kenneth. The ParaView tutorial.---Mountain View: Sandia National Laboratories,2018.---158c.
\bibitem{gmesh} Guezaine Christophe. Gmsh Reference Manual/Guezaine Christophe,Remacle Jean-Francois.---International Journal for Numerical Methods in Engineering 79(11), 2021.---389c.
\bibitem{ns} Barrett J.W. A Stable Parametric Finite Element Discretization of Two-Phase
Navier-Stokes Flow/Barrett J.W.,
Garcke H., Nuernberg R. ~// J. Sci. Comput., 2014. --- 42c.
\bibitem{meshpy} MeshPy Documentation [Электронный ресурс]~--- \\Режим доступа: https://documen.tician.de/meshpy/ ---\\ Дата доступа: 05.12.2020
\bibitem{qhull} QHull [Электронный ресурс]~--- \\Режим доступа: http://www.qhull.org --- Дата доступа: 03.05.2021
\bibitem{nikulin} Никулин.~E.A. Компьютерная геометрия и алгоритмы машинной графики. --- Санкт- Петербург:БХВ Петербург,2003.---558c.
\bibitem{tricite} Triangle Documentation [Электронный ресурс]~--- \\Режим доступа: http://www.cs.cmu.edu/~quake/triangle.html ---\\ Дата доступа: 15.05.2021
\bibitem{alcite} alberta [Электронный ресурс]~--- \\Режим доступа: http://www.alberta-fem.de --- Дата доступа: 13.10.2020

\end{thebibliography}
\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ}